\section{Acknoledgements}

They say it takes a village to raise a child. In this case, it took a village to complete this research. 

Firstly, this entire project would not have been possible without the support from my advisor, Dr. Michelle Rosen. 

During my senior year of undergrad, Dr. Rosen invited Brandon Bunt and I to complete an independent study in Soft Robotics, and over 2 years later, here we are!
% Brandon and I were tasked with developing a \emph{backwards} robot, one that uncurled with actuation instead of the typical curling behavior like a finger. After one semester, we were able to fabricate a few robots exhibiting this backwards bending behavior and I decided to continue pursuing this research,

In the Fall 2022, Dr. Rosen hired several undergraduate research assitants: Elise Danko, Ruslana Bukalo, Erika Gregory, Sophia Xu, Randel Placino, and Claire Park were instrumental in iterating the fabrication process and experimentation procedures, and each of them were always willing and able to test out my new, wacky ideas to create this robot. 

The experimentation equiptment would not have been possible without the guidance of Michael Giglia, who taught me more than words can describe about designing robust experimentation systems and robotics.

In 2023, Dr. Rosen hired Isaiah Rivera who upgraded the electronics for pressure rig to provide more precise control. For measuring the bending behavior of the robots, it would not have been possible without the software written by Joya Debi, Isaiah Rivera, and Ani Vardanyan. 

The background research was possible through James Malin, the librarian, who showed me how to navigate the world of academic research. 

I would not have gotten through these last 2 years at Cooper without the support from the Deans, Lisa Shay and Barry Shoop. 

I would like to thank the person who found me at the end of each day around 11:30pm, who wiped my chalkboard, cleaned my lab bench, swept the floors, and took out the trash in the lab each day. Knowing you would always be there with a smile at the end of each long day made it all possible. 

I would like to thank my friends, each one of you made this possible for me. Thank you Douglas Thornhill, Catherine Van West, Jacob Koziej, Jonathan Lu, Ridwan Hussain, and Alice Cruz. 

Finally, I would like to thank my parents and grandparents, who always believed I could succeeed in STEM and who made it possible for me to live out my dreams of living in New York City and studying robotics. 